Guided Proofreading of Automatic Segmentations for Connectomics\\~\\\textit{Supplemental Material}

### 2017-11-13 paper/supplemental/userstudy.tex
Update plots for the supplemental material.
Latest updates including supplemental for submission and the arXiv versions.
Update supplemental.

\end{tabular}
\hspace{2mm}
\hrule
}
\label{tab:participants}
\end{table}

@@

After the experiment, we acquired subjective responses using the NASA-TLX task load index (figure~\ref{fig:nasatxl}). We performed ANOVA to test for statistical significance~\cite{shaffer1995}. Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading but the analysis did not yield any significance.

>>>>

\end{tabular}
\hspace{2mm}
}
\label{tab:participants}
\end{table}

\subsection{User Interface}

\CHANGED{We integrate guided proofreading into an existing large data connectomics workflow. The web-based system is designed with a novice-friendly user interface (Fig. 5 in the paper, and the supplemental video). We show the current labeling of a cell boundary outline and its proposed correction overlayed on EM image data. The user cannot distinguish the current labeling from the proposed correction to avoid selection bias. We also show a solid overlay of the current and the proposed labeling. In addition, we show the image without overlays to provide an unoccluded view. User interaction is simple and involves one mouse click on either the current labeling or the correction. After interaction, the next potential error is shown.}

@@

After the experiment, we acquired subjective responses using the NASA-TLX task load index (Figure~\ref{fig:nasatxl}). We performed ANOVA to test for statistical significance~\cite{shaffer1995}. Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading but the analysis did not yield any significance. \CHANGED{This is unsurprising as the user interface was the same for both groups.}
